\section*{Personal Projects}
{\color{violet}*}
\footnotesize
Closed source code projects can be requested, the others are available on my GitHub.\\\\
\normalsize
\tech[*]
  {Conference Bot}
  {.NET Core}
  {I developed a Discord bot using .NET Core as a Gig on the Fiverr platform.
   It allows the user to handle conferences in a more convenient way by permitting/revoking speech permission based on a priority queue.}
\tech
  {Curriculum Vitae}
  {LaTeX}
  {This curriculum was written using LaTeX, the main purpose of the project was to learn how to write aesthetically pleasing and well structured LaTeX documents. In addition the CV builds automatically when new code gets pushed to the repository, using GitHub Actions CI/CD.}
\tech[*]
  {TeraToolbox Modules}
  {NodeJS, CryptoJS}
  {I have contributed, and wrote, multiple scripts for the open source project TeraToolbox. While working on this project I learned a lot about how packet traffic works, how to capture and parse it, and I have solid foundations on how a Networking Proxy works. In addition I learned how data serialization and encrypting/decrypting works.}
\tech[*]
  {Web Scrapers}
  {Python, JavaScript}
  {I wrote multiple scrapers to suffice my needs for data. Whether is data for statistics or aggregating manga libraries, I can write a quick scraper on the fly using Python or JavaScript (Cheerio).}
\tech
  {Basic Neural Network}
  {Rust}
  {I wrote a neural network which learns how to compute a logical X-OR, with no prior knowledge. The neural network was written from scratch, using no libraries except the standard library, and the purpose was to learn in detail how a network is structured.}
\tech
  {Dungeon Crawler}
  {Rust}
  {While exploring the Rust programming language, I developed a 2D Dungeon Crawler videogame, where I applied the best practices and learned how to structure medium-sized projects. The main purpose of the project was becoming proficient at the language.}
  