\section*{Experience with Technologies}
\tech
  {Documentation}
  {Jira Confluence, LaTeX, JavaDoc}
  {I have the good habit of keeping my code well documented using JavaDoc or similar, when possible, or simple comments in alternative. At work I also learned to write both technical documentation and end-user documentation using Jira's Confluence platform.\\
  In addition I also have experience using LaTeX for technical/scientific documents, as a matter of fact this curriculum is written using \LaTeX .}
\tech
  {Version Control Systems}
  {Git, SVN, Mercurial}
  {On a daily basis I find myself using Git to manage project repositories, whether it is at work, for my personal projects or projects I do in my free time with friends. I can manage branching, pull requests and set up CI/CD pipelines without any issues. In addition I have experience using SVN and Mercurial in my past work experience.}
\tech
  {Operating Systems}
  {Windows, Linux}
  {I have a wide knowledge of Linux distributions, starting from stable long-term support ones like Debian and Gentoo, all the way to rolling-release like Arch Linux and Ubuntu.\\
  The terminal is not something I fear. During my education I learned to configure firewalls with IP Tables and how to deploy and configure Linux servers, mostly Debian.\\
  Windows is my main operating system, which is also the one I am using currently at work, I have learned how the environment works and how to manage configurations and services.}
\tech
  {.NET Environment}
  {C\#, ASP.NET Core, WinForms}
  {I have experience in developing console applications using C\# (.NET), developing RESTful API using ASP.NET Core and developing native desktop applications using WinForms.}
\tech
  {Spring Framework}
  {Java, Hibernate}
  {At my current job we are using Spring, in addition to Angular Front-End, to develop large scale medical applications. In addition to the base framework we are using Hibernate to manage more conveniently data persistence.}
\tech
  {Node.JS}
  {React, Angular, Express, Electron}
  {In regard to the node stack, I have been using it to write both Front-End and Back-End applications. Whether I am using JavaScript or TypeScript is completely transparent, I have been using both to develop web applications with the React + Express stack.\\
  In addition I have experience in porting WebApps to a Desktop application using Electron or React Native.}
